Compositional Quantitative Resource Analysis of C Programs

### 2014-06-24 paper/main.tex
describe meaning of triples

>>>>

\paragraph{Semantic meaning of triples.}

We already gave an intuition of the meaning of judgements
derived in the logic, to make it formal we define the
\emph{resource safety} $\safe n P S \cont$ of an assertion
and a program configuration as
\begin{align*}
  \forall \state \, \cost \, m \, \cost' .\,&
  (m \le n \land P(\state) \le \cost \land
    (\state, S, \cont, \cost) \smallstep{M}^m (\_, \_, \_, \cost')) \\
  &\implies 0 \le \cost'.
\end{align*}
This predicate is step indexed by an integer $n$ that will
be used in the soundness proof for the function call and
loop cases.  The constraint $0 \le \cost'$ imposed by the
definition makes sure that the program does not stop on a
resource error.  However, it does not rule out memory safety
errors or assertion failures, this is because our logic does
not prove any safety or correctness theorems but only
focuses on resource usage.

The safety of a continuation $\cont$ is defined using three
assertions, one for each of the possible outcome of a program
statement.  We denote it by $\safeK n B R Q \cont$ and define
it to be
\begin{align*}
& \safe n B {\code{break}} \cont \\
\land& \safe n {\lambda \state.\,R\,(\state(x))} {\code{return}~x} \cont \\
\land& \safe n Q {\code{skip}} \cont.
\end{align*}

We can now define the \emph{semantic validity} of a function-context
free logic judgement $B; R \vdash \htriple P S Q$ as follows
\begin{align*}
\valid n B R P S Q := \\
\forall m\, \cont .\,& (m \le n \land \safeK m B R Q \cont) \\
&\implies \safe m P S \cont.
\end{align*}
We use this validity definition to give a meaning to function
specifications $\forall z \, \vec v \, v.(P_f \, z \, \vec v,
Q_f \, z \, v)$ as follows
$$
  \forall z \, \vec v \, n .\,
  \valid n \bot {Q_f \, z} {P_f \, z \, \vec v} {S_f} \bot ,
$$
where $S_f$ is the body of the function $f$.
